\documentclass[../../../main.tex]{subfiles}
\begin{document}

\chapter{Evaluation}
Prototype 1 has been quite successful. Out of the original success criteria:
\begin{itemize}
	\item Plot a explicit function in $x$
	\item Plot multiple functions on the same plot
\end{itemize}
,both have been fulfilled and been extended. I have been able to plot an explicit function in terms of $y$ and made a Normal Distribution Function. I can plot all of the functions that I originally wanted quite accurately, with the only inaccuracies due to the programming language and not my algorithms.\\
I showed this prototype to my stakeholders and they said that they \textit{``It looks impressive so far''} and \textit{``I like the simplistic and uncluttered look of it and I hope that you keep it that way''}. Matthew asked for a new feature where you can \textit{``hide and show any function''} and Miss Naguthney asked for a feature where you can \textit{``see the coordinates of the point your cursor is at''}. So I will add these to the list of requirements.
\\
However this project has presented some problems in terms of time. It is clear that a third prototype will not happen in the time available and some of prototype 2 will not happen either. This is the new requirements for prototype 2:
\begin{itemize}
	\item Let the user input functions
	\item Zoom in/out of the graph
	\item Pan around the graph
	\item Save plots as pictures
	\item Show/Hide functions (suggestion from a stakeholder)
	\item Show coordinates in top left of pane (suggestion from a stakeholder)
\end{itemize}
From talking to my stakeholders, these are the key things that they want in a graphing program and as such these are the things that I will definitely implement. If I have time I will implement the other features.
\newpage
\end{document}